---
title: "Access different issues of different instances"
author: "ixpantia"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Access multiple Gitea instances}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
editor_options: 
chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Gitea is a community managed, lightweight code hosting solution  were projects
and their respective git issues can be managed  <https://gitea.io>. This
package gives an interface to the 'Gitea' API to  access and manage
issues, issues of differents instances directly in R.

## Get information about your issues of differents instances

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r eval FALSE}
base_url <- Sys.getenv("URI")
api_key <- Sys.getenv("TOKEN")
owner <- Sys.getenv("USUARIO")
repo1 <- Sys.getenv("REPOSITORIO_1")
repo2 <- Sys.getenv("REPOSITORIO_2")
repo3 <- Sys.getenv("REPOSITORIO_3")

base_local <- Sys.getenv("URL_LOCAL")
owner_local <- Sys.getenv("OWNER_LOCAL")
api_key_local <- Sys.getenv("TOKEN_LOCAL")

instancia_1 <- c(base_url, api_key, owner, repo1)
instancia_2 <- c(base_url, api_key, owner,repo2)
instancia_3 <- c(base_local, api_key_local, owner_local,repo3)

lista <- list()
lista$inst1 <- instancia_1
lista$inst2 <- instancia_2
lista$inst3 <- instancia_3

diff_inst_open_issues <- function(lista_intancia) {
   # lista_resultado <- data.frame(titulo = character(0), contenido = character(0))
     if (missing(lista_intancia)) {
        warning("Please add a valid list")
        } else {
            try({
            for (ins in lista) {
               issues <- (gitear::get_issues_open_state(ins[1], ins[2], ins[3],
                                                ins[4]))
           
             for(i in 1:length(issues)){
                 if(!is.na(issues[i, 5])){
                    print (c(issues[i, 5], issues[i, 6]))
                 }
                }
            }
        })
    }
}

diff_inst_open_issues(lista)
```

