---
title: "Access Gitea from R"
author: "ixpantia"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Acess Gitea from R}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Gitea is a community managed, lightweight code hosting solution  were projects
and their respective git repositories can be managed  <https://gitea.io>. This
package gives an interface to the 'Gitea' API to  access and manage
repositories, issues and organizations directly in R.

## Starting with `gitear`

If you want to start using the functions from `gitear` you should first go to
your ixplorer and create an API KEY. You will find this under your avatar,
configuration, application and then generate a new token.

Be aware that you should save this token somewhere because its shown just once.

This is going to be your API TOKEN.

Then you can use a function like this:

```{r, eval = FALSE}
## Credenciales
key <- "gfdsgfd8ba18a866bsdfgsdfgs3a2dc9303453b0c92dcfb19"
url_ixpantia <- "https://secure.ixpantia.com"

## Prueba funcion
issues <- get_issues(base_url = url_prueba,
                       api_key = llave,
                       owner = "ixpantia",
                       repo = "ixmandash")
```




## Get information about your projects

```{r, eval=FALSE}
organizations <- get_an_organization("ixpantia", base_url, api_key)
```
